---
title: "Base R- Weekly Assignment #2"
author: "Amanda Mae Woodward"
date: "2022-10-03"
output: html_document
---
# Set Up
1. Load the tidyverse library. 
```{r}
library(tidyverse)
```
#√
2. Load the billboard data. 
```{r}
data("billboard")
```
#√
3. What type of data is this? (e.g. describe what's in the dataset.)
```{r}
#via '?billboard'
#the dataset contains song rankings for billboard songs top 100 in the year 2000

summary(billboard)
```
#√
4. Print the column names from this dataset. 
```{r}
colnames(billboard)
#√
```

5. Print the first 5 entries in the dataset. 
```{r}
head(billboard,5)

```
#√

# Practice
1. Create a subset of data that has Jay-Z as the only artist. How many songs are in it?
```{r}
subset(billboard, billboard$artist=="Jay-Z")

#the subset contains 5 songs

```
#√
2. In the original dataset, use filter to find information about the song "All the small things." What was the highest position this song reached on the billboard 100? 
```{r}
billboard %>% filter(track== "All The Small Things")

ATST_dat<- billboard %>% filter(track== "All The Small Things")
summary(ATST_dat)

#the highest position the song reached on charts was 6

```
#√
3. Create a subset of data for songs Tim McGraw sang. Summarize the data for wk 1.
```{r}

subset(billboard, billboard$artist== "McGraw, Tim")
McGraw_dat<- subset(billboard, billboard$artist== "McGraw, Tim")
summary(McGraw_dat$wk1)
```
#√
