---
title: "Base R- Weekly Assignment #1"
author: "Amanda Mae Woodward"
date: "2022-09-28"
output: html_document
---

1. Name the four panels in R Studio and offer a brief description of each.
top left: R markdown (This is where we put our stuff that we want to save)
top right: Global environment (This is everything like an overview, contains variables, datasets, vectors, and functions)
bottom left: Console (This is where we run code, its like a scratch paper, and you can install.packages and view)
bottom right: Everything else (This has everything else that you need)

2. Create a code chunk. Write your favorite number in it. 
```{r}
13
```

3. Add thirty-seven to six
```{r}
37+6
```

4. evaluate the following: six times four is equal to twenty-four
```{r}
6*4 ==24
```

5. What's the difference between an "and" and an "or" statement? 
The difference between an "and" and an "or" statement is that that and "and" statement is used when both things need to be true, and an "or" statement is used when only one has to be true.

6. Create an "and" statement for the following sentence: three is less than five and tree is the same as oak. 
```{r}
3<5 & "tree"=="oak"
```

7. Create a variable called "dinner" that contains your favorite thing to eat for dinner.
```{r]
dinner <- "sushi"
```

8. write out all numbers between 50 and 200
```{r}
seq(50,200,1)
```

9. print every odd number between 1 and 300. 
```{r}
rep(seq(1,300,2),1)
```

10. repeat the phrase "i'm excited for fall" five times
```{r}
rep("i'm excited for fall",5)
```

