---
title: "Base R- Weekly Assignment #1"
author: "Amanda Mae Woodward"
date: "2022-09-28"
output: html_document
---

1. Name the four panels in R Studio and offer a brief description of each.

##top left: R Markdown: -- where we put stuff we want to save

##top right: Global Environment: 
--has everything (overview) 
--contains variables, data sets, vectors, functions

##bottom left: Console 
--where code runs (see output here depending on settings) 
--errors 
--scratch paper (doesn't save) 
--install .packages and view

##bottom right: everything else

2. Create a code chunk. Write your favorite number in it. 

```{r}

8

```

3. Add thirty-seven to six

```{r}
37+6
```

4. evaluate the following: six times four is equal to twenty-four
```{r}
(6*4)==24
```

5. What's the difference between an "and" and an "or" statement? 

"And" statement-- both things have to be true
"Or" statement-- one or more of the things has to be true

6. Create an "and" statement for the following sentence: three is less than five and tree is the same as oak. 

```{r}
3<5 & "tree"== "oak"

```

7. Create a variable called "dinner" that contains your favorite thing to eat for dinner. 

``` {r}
dinner<- "soup and a baked sweet potato"
```

8. write out all numbers between 50 and 200

```{r}
50:200
```

9. print every odd number between 1 and 300. 

```{r}
seq(1,300,2)
```

10. repeat the phrase "i'm excited for fall" five times

```{r}
rep("i'm excited for fall", 5)
```
