---
title: "Base R- Weekly Assignment #2"
author: "Amanda Mae Woodward"
date: "2022-10-03"
output: html_document
---

# Set Up
1. Load the tidyverse library. 
```{r}
```
# you didn't load the tidyverse library

2. Load the billboard data. 
```{r}
data("billboard")
```
#this wouldn't load if you didn't load the library 
#√
3. What type of data is this? (e.g. describe what's in the dataset.)
```{r}
class(billboard$artist)
class(billboard$track)
class(billboard$date.entered)
class(billboard$wk1)
#there are characters/labels, date, and numeric in the data set
```
#√-; ?billboard would have provided these answers
 
4. Print the column names from this dataset. 
```{r}
colnames(billboard)
```
#√
5. Print the first 5 entries in the dataset. 
```{r}
billboard[5,]
```
#√
# Practice
1. Create a subset of data that has Jay-Z as the only artist. How many songs are in it?
```{r}
billboard %>% filter(artist=="Jay-Z")
subset(billboard, billboard$artist== "Jay-Z")
```
#how many songs? 
#√
2. In the original dataset, use filter to find information about the song "All the small things." What was the highest position this song reached on the billboard 100? 
```{r}
billboard %>% filter(track=="All The Small Things")
## The highest position was 6##
```
#√
3. Create a subset of data for songs Tim McGraw sang. Summarize the data for wk 1.
```{r}
subset(billboard, billboard$artist=="McGraw, Tim")

summary(subset(billboard, billboard$artist=="McGraw, Tim", "wk1"))
```
#√

