---
title: "Optional Dataset Manipulation Quiz"
author: "Amanda Mae Woodward"
date: "2022-11-03"
output: html_document
---
This quiz is meant to help you synthesize materials we've covered in class. If you'd prefer to use other functions, that's okay too. 
You should see the following variables: 
subj- subject number
condition- experimental or control
stroop- an accuracy score for the stroop task (30 trials)
nback- an accuracy score for the n back task (recalling a number/object a given number of trials back;50 trials)
ravens- score on raven's progressive matrices (25 trials)

People are assigned to either complete a cognitive training task (to improve memory) or to have no training. We have  

Upload the psy4960-Quiz2.csv file.
```{r}

```

1. Take a summary of the full dataset.
```{r}

```

2. What kind of data do you have (wide or long?). How do you know?

3. Check the type of data presented in the condition column. Make sure this variable is a factor
```{r}

```

4. Create a new column called Stroop Accuracy.
Label those who have a higher than average score at t1 "high EF", those below average "low EF" and those at average "Average EF" (Note: EF stands for executive function). 
```{r}

```

5. Create a dataset containing participants' nback scores in long format. (Note: you should keep all other variables)
```{r}

```
6. Returning to the original dataset, create a column indicating the difference between the two ravens scores. 
```{r}

```

7. Based on #6, create two subsets of data: 1 where the ravens difference score is positive and one where it is negative
```{r}

```