---
title: "Quiz 1"
author: "Amanda Mae Woodward"
date: "2022-10-11"
output: html_document
---
This quiz will cover everything we've covered in Base R. 
1. Open the tidyverse library.
```{r}
library(tidyverse)
```
#√

2. Open the starwars dataset.
```{r}
data("starwars")
```
#√
3. Create a subset of data that contains only the humans from the starwars franchise.
```{r}
subset(starwars, starwars$species == "Human")
```
#√
4. In this subset of data, who is the tallest character?
```{r}
summary(subset(starwars, starwars$species == "Human"))
starwars %>% filter(height==202.0)
```
#√
5. In this subset of data, print the information about the character in the third row. 
```{r}
subset(starwars, starwars$species == "Human")[3,]
```
#√
6. In the full starwars dataset, calculate the average mass for the masculine characters. 
```{r}

SWMale<-subset(starwars, starwars$gender=="masculine")
mean(SWMale$mass)
summary(SWMale)
```
#√
7. Create a dataset that contains only the characters and the films that they appeared in from the full dataset.
```{r}
cbind(name<-starwars$name, films<-starwars$films)
```
#√- this works, but the assignments you are doing within the column aren't doing anything. currently, the columns have no name

8. Create a new column in the starwars dataset that contains a "ranking" of all characters (Note: you don't have to actually rank them. Just fill the column in with the numbers 1-87)
```{r}
starwars$rank<-1:87
```
#√
9. Create a subset of data for the characters from Naboo. How many characters are from Naboo? 
```{r}
subset(starwars, starwars$homeworld == "Naboo")
summary(subset(starwars, starwars$homeworld == "Naboo"))
##11 of them##
```
#√
10. How many droids are in the full dataset? 
```{r}
subset(starwars, starwars$species== "Droid")
## 6 of them##
```
#√
